\textit{MSF: Modulated Sub-graph Finder}

### 2018-03-27 MSF_Paper_FA.tex
Corrections

Simulation testing was also conducted on \texttt{MSF}. For each time-point, one \texttt{MSF} identified sub-graph was taken. A random graph was generated with the same number of genes as the sub-graphs and the predicted sources were counted. The objective
was to find less sources in the simulated sub-graphs than observed in the real sub-graphs identified by
\texttt{MSF}. Simulation results showed a chance of $<$10$\%$
of the 1000 random sub-graphs generated to get more sources than observed.

>>>>

 To test \texttt{MSF's} correctness simulation was also conducted. For each time-point, one \texttt{MSF} identified sub-graph was taken. A random graph was generated with the same number of genes as the sub-graphs using the same interaction file and the identified sources were counted. The objective
 was to find less sources in the simulated sub-graphs than observed in the real sub-graphs identified by
 \texttt{MSF}. Simulation results showed a chance of $<$10$\%$
 of the 1000 random sub-graphs generated to get more sources than observed.
